Wigglyhedra

### 2024-11-13 FPSAC25/wigglyhedraFPSAC.tex
update affiliation and grants

%% define your authors in the usual way
%% use \addressmark{1}, \addressmark{2} etc for the institutions, and use \thanks{} for contact details
%% for more than 3 names, use the Oxford comma: One Author, Two Author, Red Author, \and Blue Author
\author{Asilata Bapat\thanks{\href{mailto:asilata.bapat@anu.edu.au}{mailto:asilata.bapat@anu.edu.au}. Supported by the Australian grants DE240100447 and DP240101084.}\addressmark{1} \and Vincent Pilaud\thanks{\href{mailto:vincent.pilaud@ub.edu}{mailto:vincent.pilaud@ub.edu}. Supported by the French--Austrian grant PAGCAP (ANR-21-CE48-0020 \& FWF I 5788) and by the Spanish grant PID2022-137283NB-C21.}\addressmark{2}}

%% then use \addressmark to match authors to institutions here
\address{\addressmark{1}The Australian National University, Canberra, Australia \\ \addressmark{2}Universitat de Barcelona, Spain}

>>>>

%% define your authors in the usual way
%% use \addressmark{1}, \addressmark{2} etc for the institutions, and use \thanks{} for contact details
%% for more than 3 names, use the Oxford comma: One Author, Two Author, Red Author, \and Blue Author
\author{Asilata Bapat\thanks{\href{mailto:asilata.bapat@anu.edu.au}{mailto:asilata.bapat@anu.edu.au}. Supported by the Australian grants DE240100447 and DP240101084.}\addressmark{1} \and Vincent Pilaud\thanks{\href{mailto:vincent.pilaud@ub.edu}{vincent.pilaud@ub.edu}. Supported by the French--Austrian grant PAGCAP (ANR-21-CE48-0020 \& FWF I 5788), and by the Spanish grants PID2022-137283NB-C21, 2021 SGR 00697 and CEX2020-001084-M.}\addressmark{2}}

%% then use \addressmark to match authors to institutions here
\address{
	\addressmark{1}The Australian National University, Canberra, Australia \\ 
	\addressmark{2}Universitat de Barcelona \& Centre de Recerca Matemàtica, Spain
}
